### 2021-12-09 paper.tex
feat: Add boilerplate

\documentclass{scrarticle}

\begin{document}

\title{Quantum Computing}
\author{Jakob Waibel}
\date{}

\maketitle

\tableofcontents

\end{document}

### 2021-12-11 paper.tex
feat: Add documentclass, introduction and some boilerplate

@@
-\documentclass{scrarticle}
+\documentclass[aps,twocolumn,preprintnumbers]{revtex4}
 
@@
 
-\title{Quantum Computing}
+\title{Quantum Computing and its Implications on Digital Security}
+
 \author{Jakob Waibel}
-\date{}
+
+\affiliation{\it Stuttgart Media University, 70569 Stuttgart}
+
+\date{\today}
+
+\begin{abstract}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Donec in ex ut mauris mollis dictum.
+Aenean tempor scelerisque lectus, eu varius ex ullamcorper ac.
+Nulla quis mattis tellus.
+Vivamus imperdiet ante sit amet tellus dapibus imperdiet.
+Quisque iaculis consequat cursus.
+Morbi in tempor neque, eu aliquet est.
+Pellentesque dapibus nulla id sem scelerisque eleifend.
+Ut tincidunt ex nec erat pharetra pretium.
+Vivamus bibendum quam id nunc fermentum tincidunt.
+Duis congue semper nulla sed porttitor.
+Morbi feugiat suscipit pellentesque.
+Nullam eget velit vel ligula suscipit convallis.
+\end{abstract}
 
@@
 
-\tableofcontents
+\begin{section}{Introduction to quantum computing}
+
+% https://www.technologyreview.com/2019/01/29/66141/what-is-quantum-computing/
+
+Quantum computers utilize qubits to represent information. 
+Instead of working with a stream of electiral or optical signals representing 1s and 0s, 
+quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
+This effect is called superposition. To put qubits into superposition, 
+researchers manipulate qubits in different ways. Like in quantum mechanics, 
+a measurement determines the state. Once qubits are measured, 
+it's quantum state immediately collapses to either 1 or 0.
+
+Entanglement causes pairs of qubits to entangle.
+This results in those qubits having a similar quantum state at all times.
+If the state of one of those entangled qubits changes,
+the other one will instantaneously change its state as well.
+This entanglement allows quantum computers to increase it's computational power exponentially,
+rather than linearly on regular computers.
+
+Qubits quantum behavious is determined to decay.
+This effect is known as the scientific term "decoherence".
+It describes the quantum state being extremely fragile.
+The slightest disturbance can cause a qubit to loose its state of superposition.
+These disturbances can be created by vibrations or change of temperatures.
+Disturbances are also refered to as "noise" in quantum computer terminology.
+This is the reason why qubits and quantum computers are held in extremly protected environments, 
+often fridges or vacuum chambers.
+To compensate for this noise, 
+thousands of standard qubits will be needed to create a reliable qubit, 
+refered to as a "logical" qubit. 
+To set this into context, 
+according to Siobhan Roberts in MIT Technology Review, 
+the most qubits used in a quantum computer, 
+% https://www.technologyreview.com/2021/11/17/1040243/quantum-computer-256-bit-startup/
+as of November 17, 2021 are 256 in a quantum computer by the Boston startup QuEra Computing.
+
+Since the first proposals revolving around quantum computers back in 1980 by Yuri Manin and Richard Feynman in 1981,
+the term "quantum supremacy" is used to denote the point at which a quantum computer can complete a mathematic calculation that is beyond reach of even the most powerful supercomputer.
+It is unclear how many qubits will be needed to achieve this because researchers keep finding new algorihtms to boost the performance of classical computers and supercomputing hardware is getting better as well.
+
+\end{section}
+
+\begin{section}{Experimental Realizations of Quantum Computers}
+
+\end{section}
 

### 2021-12-11 paper.tex
feat: Add draft about realizations and quantum algorithms

@@
 \documentclass[aps,twocolumn,preprintnumbers]{revtex4}
+% \documentclass[aps,preprintnumbers]{scrartcl}
 
@@
 
-\begin{section}{Introduction to quantum computing}
+\begin{section}{Introduction}
 
@@
 rather than linearly on regular computers.
+According to MIT Technology Review, a quantum computer equipped with 300 qubits could represent more states than there are atoms in the observable universe.
 
@@
 as of November 17, 2021 are 256 in a quantum computer by the Boston startup QuEra Computing. 
+There is not a single way to build a quantum computer. 
+Instead, different approaches can be followed to develop machines utilizing quantum effects for computing.
 
@@
 
+There are different attempts of realizations of quantum computers.
+Those different approaches have different advantantages and challenges. 
+Some of those realizations, especially the ones important with regards to digital security, 
+are summarized in the following:
+
+\begin{subsection}{Ion Traps}
+The ion trap quantum computer encodes data in energy states of ions and in vibrational modes between ions. 
+Conceptually, each ion is operated by a sepearte laser. 
+A preliminary analysis demonstrated that Fourier transforms can be evaluated with the ion trap computer. 
+This, in turn, leads to Shor's factoring algorithm, 
+which is based on Fourier transforms.
+\end{subsection}
+
+\begin{subsection}{Nuclear Magnetic Resonance}
+A Nuclear Magnetic Resonance (NMR) computer consists of a capsule filled with a liquid and an NRM machine. 
+Each molecule in the liquid is an independet quantum memory register. 
+Computation proceeds by sending radio pulses to the sample and reading its response. 
+Qubits are implemented as spin states of the nuclei of atoms comprising the molecules. 
+In contrast to the Ion Trap computer, 
+a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register. 
+NMR computers have been achieving the most accomplishements in quantum computing so far, 
+as they can solve non-polynomial complete problems in a polynomial time.
+\end{subsection}
+
+\begin{subsection}{Josephson Junctions}
+A Josepson junction quantum computer is a Cooper pair box,
+which is a small superconducting island electrode weakly coupled to a bulk superconductor. 
+Weak coupling between the superconductors create a Josephson junction between them which behaves as a capactor. 
+If the Cooper box is as small as a quantum dot, 
+the charging current breaks into discrete transfer of individual Cooper pairs. 
+Ultimately, it is possible to just transfer a single Cooper pair across a junction. 
+Qubits in Josephson junction quantum computers are controlled electrically which results in them being interesting for future developments.
+\end{subsection}
+
 \end{section}
 
+% Maybe change this into something like: Evaluation of Post-Quantum Security Mechanisms
+\begin{section}{Quantum computing algorithms and their effects on current security mechanisms}
+As discussed earlier, quantum computers could eventually reach the state of quantum superiority, 
+in which the quantum computer can perform tasks no regular computer could ever compute.
+This implies that the quantum computer could also solve problems which a regular computer could not solve so far.
+Which problems can be solved and which security mechanisms are affected will be discussed in this following section.
+
+% Look into paper for this. The paper has a perfect level for our own research.
+\begin{subsection}{Shor's algorithm}
+% Think about talking about quantum gates
+Shor's algorithm is a polynomial-time quantum computer algorithm for integer factorization.
+Essentially it solves the following problem: 
+Given an integer $N$m find its prime factors. 
+On a quantum computer, to factor an integer $N$, 
+Shor's algorithm runs in polynomial time. 
+Using quantum gates demonstrates, 
+that integer-factorization can be solved on a quantum computer an is consequently in the complexity class BQP, 
+which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $1/3$ for all instances. 
+This algorithm is almost exponentially faster than the most efficient known classical factoring algorithm, the general number field sieve which is the most efficient known factoring algorithm on regular computers.
+The efficiency of Shor's algorithm is due to the efficiency of the quantum Fourier transform and modular exponentiation by repeated squearings. 
+If a quantum computer with a sufficient number of qubits could operate without succumbing to quantum noise and other quantum-decoherence phenomena, 
+Shor's algorithm could be used to break public-key cryptography schemes, 
+such as the RSA scheme or the Diffie-Hellman key exchange.
+
+% Maybe refer to the first nmr attempt of 2001. Access to the paper is given.
+So far, the largest number factorized using Shor's algorithm, 
+as of 2019 is the number 21 factored back in 2012. 
+The integer 35 was attempted in 2019 on an IBM Q System One, 
+but the algorithm failed.
+
+% Eventually add math for Shor's algorithm
+\end{subsection}
+
+% Consider paper for this section as well
+\begin{subsection}{Grover's algorithm}
+% Think about writing either 128 bit or 128-bit in the whole paper
+Grover's algorithm, devised by Lov Grover in 1996,
+refers to a quantum algorithm for performing unstructered search. 
+The analogous problem in classical computing cannot be solved in fewer than $O(N)$ evaluations. 
+Grover's algorithm is achieving the same goal in $O(\sqrt{N})$. 
+In contrast to Shor's algorithm providing exponential speedup, 
+Grover's algorithm only provides quadratic speedup. 
+Considering Grover's algorithm could be used to brute-force a 128-biy symmetric key in roughly $2^{64}$ iterations, 
+or a 256-bit key in roughly $2^{128}$ iterations.
+\end{subsection}
+
+\end{section}
+
+\begin{section}{Post Quantum Cryptography}
+Additionally, it will be discussed what defines a quantum-proof algorithm. 
+Increasing the key size from e.g. 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm.
+The goal is the same as it was before quantum computers ermerged.
+The operations to crack the security mechanisms have to become infeasable to perform.
+
+Another approach would be to develop new algorithms using more complex trapdoor functions even quantum computers could not possibly crack in a feasible amount of time. 
+Researchers are working in areas like lattice-based cryptography and supersingular isogeny key exchange.
+\end{section}
+% Conclusion: I see it as an improvement, not as dangerous
 \end{document}

### 2021-12-12 paper.tex
feat: Add some notes on experimental realizations of quantum computing

@@
 which is based on Fourier transforms.
+
+Also refered to as "trapped ion quantum computer". 
+The fundamental operations of a quantum computer have been demonstrated experimentally with the currently highest accuracy in trapped ion systems. 
+Trapped ion computers are researched because they could be used for a large-scale quantum computer.
+Scaling the ion trap to a large number of qubits could be accomplished by combining multiple ion traps into an array and transporting ions between them. 
+As of 2018, the largest number of particles to be controllable entangled is 20 trapped ions. 
+In 2021, researchers from the University of Innsbruck presented a quantum computing demonstrator that fits inside two 19-inch server racks, 
+the world's first qualirt standards meeting compact trapped ion quantum computer.
+
+Challenges for ion traps include initialization of the ion's motional states, 
+the relatively brief lifetimes of the photon states and the decoherence which is is caused when the qubits interact with the external environment undesirably.
 \end{subsection}
@@
 as they can solve non-polynomial complete problems in a polynomial time.
+
+Initially the approach was to use the soin properties of atoms of particular molecules in a liquid sample as qubits - 
+this is known as liquid state NMR (LSNMR). 
+This approach has since been superseeded by solid state NRM (SSNMR) as a means of quantum computation.
+
+Solid state NMR (SSSNMR) differs from LSNMR in that we have a solid state sample, 
+for example a nitrogen vacancy diamond lattice rather than a liquid sample. 
+This has many advantages such as lack of molecular diffusion coherence, 
+lower temperatures can be achieved to the point of suppressing phonon decoherence and a greater variety of control operations that allow us to overcome one of the major problems of LSNMR that is initialisation.
+Moreover, as in a crystal structure we can localize precisely the qubits, 
+we can measure each qubit individually, 
+instead of having an ensemble measurement as in LSNMR.
+
+More recent work shows that all experiments in liquid state bulk ensemble NMR quantum computing to date do not possess quantum entanglement, 
+thought to be required for quantum computation. 
+Hence NMR quantum computing experiments are likely to have been only classical simulations of a quantum computer. 
 \end{subsection}
@@
 Qubits in Josephson junction quantum computers are controlled electrically which results in them being interesting for future developments.
+
+In Physics, the Josephson effect is a phenomenon that occurs when two superconductors are placed in proximity, 
+with some barrier or restriction between them. 
+The Josephon effect produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
+This current thorught the junction occurs by quantum tunneling. 
+This is used to create a non-linear inductance which is essential for qubit design, 
+as it allows a design of anharmonic oscialltors. 
+A quantum harmonic oscillator cannot be used as a qubit, 
+as there is no way to address only two of its states. 
 \end{subsection}

### 2021-12-12 paper.tex
feat: Add challenges in quantum computing, lattice based cryptography and conclusion

@@
 
+\begin{section}{Challenges in Quantum Computing}
+As of 2021, there are some challenges in quantum computing researchers are working on:
+
+\begin{itemize}
+    \item Quantum algorithms are mainly probabilistic. 
+    This means that in one opeartion a quantum computer returns many solutions where only one is correct. 
+    This trial and error for measuring and verifying the correct answer weakens the advantage of quantum computing speed. 
+    \item Qubits are susceptible to errors earlier introduced as noise. 
+    They can be affected by heat, noise in the environment, 
+    as well as stray electromagnetic couplings. 
+    Classical computers are susceptible to bit-flips. Qubits suffer form said bit-flips as well as phase errors. 
+    Direct inspection for errors should be avoided as it will cause the value to collapse, leaving it superposition state.
+    % Citation below
+    \item The difficulty of coherence is another challenge. 
+    Qubits can retain their quantum state only for a short period of time. 
+    The longest time qubits remained so far was set by Australian researchers at the University of New South Wales. 
+    Their qubits remained in superposition for a total of 35 seconds.
+\end{itemize}
+
 \end{section}
 
+\end{section}
+
+% Add maths of Shor and Grover
 % Maybe change this into something like: Evaluation of Post-Quantum Security Mechanisms
@@
 If a quantum computer with a sufficient number of qubits could operate without succumbing to quantum noise and other quantum-decoherence phenomena, 
+% Cite Kirsch here
 Shor's algorithm could be used to break public-key cryptography schemes, 
@@
 or a 256-bit key in roughly $2^{128}$ iterations.
+
+Grover's algorithm can be utilized to find a collision in a hash function in $O(sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
+% TODO: Cite brassard
+Additionally, it has been proved that it is possible to combine Grover's algorithm with the birthday paradox, 
+also known as a quantum birthday attack. 
+As a result, many of the present hash alogithms are disqualified for use in the quantum era. 
+However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant.
 \end{subsection}
@@
 
+% Research for this paragraph in a second paper
 \begin{section}{Post Quantum Cryptography}
 Additionally, it will be discussed what defines a quantum-proof algorithm. 
+Post Quantum Cryptography descrbes algorithms that are secure against quantum computing and against conventional computers.
 Increasing the key size from e.g. 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm.
@@
 Researchers are working in areas like lattice-based cryptography and supersingular isogeny key exchange.
+
+\begin{subsection}{Lattice-based Cryptography}
+This is a form of public-key cryptography that avoids the weaknesses of RSA. 
+Rather than multiplying primes, lattice-based encryption schemes involve multiplying matrices. 
+Furthermore, lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems. 
+Here, we are given as input a lattice represented by an aribtrary basis and our goal is to output the shortest non-zero vector in it.
+\end{subsection}
+
 \end{section}
 % Conclusion: I see it as an improvement, not as dangerous
+
+\begin{section}{Conclusion}
+As described before, Shor's algorithm, 
+as well as Grover's algorithm will presumably force computer scientists to improve current stadards to provide information security across areas. 
+To accomplish information security, 
+current security mechanisms such as hashing algorithms have to be improved and as a result be quantum-safe by increasing their key-length.
+The second approach mentioned in this paper is developing new, 
+quantum-secure algorithms, 
+like lattice-based cryptography. 
+Even the huge speedups quantum-computers provide don't make it feasible to crack these algorithms. 
+It is not known yet, which type of quantum computer will prevail. 
+Ion traps, Nuclear Magnetic Resonance and Josepshon Junctions are some of the most promising approaches. 
+In current systems like the IBM Q System One, 
+Josephson junctions are used in their superconducting quantum computer. 
+If this approach will prevail is unclear, 
+since quantum entanglement in this type of processor is, as of 2021, not possible yet. 
+It has to be said that quantum computers, 
+as what could be seen in the current records revolving around quantum computing, 
+are not powerful enough to form a thread to security mechanisms by now, 
+since way more qubits are needed to perform operations on large enough numbers and preserve the state of superposition long enough. 
+\end{section}
+
 \end{document}

### 2021-12-12 lerntagebuch.tex
feat: Add bibliography, citations, lerntagebuch

\documentclass{scrarticle}

\begin{document}

\title{Lerntagebuch}
\author{Jakob Waibel}
\date{\today}

\maketitle

Ich werde dieses Lerntagebuch unter anderem auch dazu nutzen, mich vor dem schreiben aufzuwärmen. 
Ich habe mich dazu entschieden das Paper iterativ zu schreiben. Ich schreibe um das Thema selber zu verstehen ein erstes Konzept mit erklärungen der verschiedenen Themen die relevant erscheinen. In der zweiten Iteration erstelle ich eine koherentere Version des bisherigen Inhalts und in der letzten Iteration überarbeite ich den Inhalt und die Formulierungen.
Die Latex-Einführung half mir dabei, Latex lieben zu lernen. Ich verwendete Latex häufig zuvor ohne wirklich zu wissen, was dahinter steckt und was ich tue. Seit der Einführung habe ich mich kontinuierlich weiter mit Latex beschäftigt bis ich zu dem Punkt gelangt bin, sogar meine Präsentation mit Hilfe von der Latex-Documentclass "beamer" zu erstellen. 
Ich habe mich dazu entschieden, die "revtex4" documentclass für mein Paper zu verwenden. Es ist ein Standard aus der Physik, welcher mich auch schon in vielen anderen Themengebieten aufgefallen ist. Durch diesen Standard ist das Paper zwar nur die hälfte der Seiten lang, sieht aber dafür so aus, wie ich mir ein Paper immer vorgestellt habe. 
Ich frage mich häufig, welches Wissen ich zitieren muss und was ich einfach so niederschreiben darf, da es keine Intellektuelle höhe benötigt hat, um diese Dinge festzustellen.

\end{document}

### 2021-12-12 paper.tex
feat: Add bibliography, citations, lerntagebuch

@@
-\documentclass[aps,twocolumn,preprintnumbers]{revtex4}
-% \documentclass[aps,preprintnumbers]{scrartcl}
+\documentclass[aps,preprintnumbers,twocolumn]{revtex4}
+% \documentclass[aps,preprintnumbers, twocolumn]{scrartcl}
+\usepackage{natbib}
+\usepackage{url}
+
+% Where I make references, put actual hyperlinks
 
 \begin{document}
-
 \title{Quantum Computing and its Implications on Digital Security}
-
+\email{mail@jakobwaibel.com}
 \author{Jakob Waibel}
@@
 
-% https://www.technologyreview.com/2019/01/29/66141/what-is-quantum-computing/
+Since Paul Benioffs and Richard Feynman's talks on quantum computing held at the first conference on the physics of computation, 
+quantum computing has become a large research area. 
+Even so large, that is has become more and more difficult to understand the basics of it and its implications on the future of computing. 
+This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
+Hence, the implications on digital security, especially cryptography will play the major role in the following paper.
 
+\end{section}
+
+\begin{section}{Quantum Computers}
 Quantum computers utilize qubits to represent information. 
@@
 This effect is called superposition. To put qubits into superposition, 
-researchers manipulate qubits in different ways. Like in quantum mechanics, 
+researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and has to obey to the same laws, 
 a measurement determines the state. Once qubits are measured, 
@@
 Entanglement causes pairs of qubits to entangle.
-This results in those qubits having a similar quantum state at all times.
+This results in those entangled qubits having a similar quantum state at all times.
 If the state of one of those entangled qubits changes,
 the other one will instantaneously change its state as well.
+This improved the processing speed of quantum computers.
+As Alamira Jouman Hajjar puts it in her Article on AIMultiple \cite{AIMultiple}, one qubit will reveal information about all the qubits said qubit is entangled with.
 This entanglement allows quantum computers to increase it's computational power exponentially,
 rather than linearly on regular computers.
-According to MIT Technology Review, a quantum computer equipped with 300 qubits could represent more states than there are atoms in the observable universe.
+According to an article of IEEE Spectrum \cite{IEEE}, a quantum computer equipped with 300 qubits could represent more states than there are atoms in the observable universe.
 
@@
 This effect is known as the scientific term "decoherence".
-It describes the quantum state being extremely fragile.
+It describes the quantum state as being extremely fragile.
 The slightest disturbance can cause a qubit to loose its state of superposition.
-These disturbances can be created by vibrations or change of temperatures.
+These disturbances can be created by vibrations, change of temperatures or related external influeces.
 Disturbances are also refered to as "noise" in quantum computer terminology.
@@
 To set this into context, 
-according to Siobhan Roberts in MIT Technology Review, 
+according to Siobhan Roberts in MIT Technology Review \cite{MIT}, 
 the most qubits used in a quantum computer, 
-% https://www.technologyreview.com/2021/11/17/1040243/quantum-computer-256-bit-startup/
 as of November 17, 2021 are 256 in a quantum computer by the Boston startup QuEra Computing. 
@@
 which is a small superconducting island electrode weakly coupled to a bulk superconductor. 
+In literature, the Josephson junctions are also refered to as superconducting quantum computers.
 Weak coupling between the superconductors create a Josephson junction between them which behaves as a capactor. 
@@
     Qubits can retain their quantum state only for a short period of time. 
-    The longest time qubits remained so far was set by Australian researchers at the University of New South Wales. 
+    According to Mavroeidis \cite{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
     Their qubits remained in superposition for a total of 35 seconds.
@@
 % Add maths of Shor and Grover
-% Maybe change this into something like: Evaluation of Post-Quantum Security Mechanisms
 \begin{section}{Quantum computing algorithms and their effects on current security mechanisms}
@@
 Shor's algorithm could be used to break public-key cryptography schemes, 
-such as the RSA scheme or the Diffie-Hellman key exchange.
+such as the RSA scheme or the Diffie-Hellman key exchange. That these algorithms could be vulnerable was already stated by Kirsch in 2015
+\cite{Kirsch2015QuantumCT}.
 
@@
 So far, the largest number factorized using Shor's algorithm, 
-as of 2019 is the number 21 factored back in 2012. 
+as of 2019 is the number 21 factored back in 2012 by Martín-López et al \cite{article}. 
 The integer 35 was attempted in 2019 on an IBM Q System One, 
@@
 
+\bibliographystyle{plain}
+\bibliography{citations}
+
 \end{document}

### 2021-12-12 paper.tex
feat Improving introduction

@@
 \documentclass[aps,preprintnumbers,twocolumn]{revtex4}
-% \documentclass[aps,preprintnumbers, twocolumn]{scrartcl}
+% \documentclass[aps,preprintnumbers]{scrartcl}
 \usepackage{natbib}
@@
 
+% Add page numbers to papers
 % Where I make references, put actual hyperlinks
@@
 This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
-Hence, the implications on digital security, especially cryptography will play the major role in the following paper.
+Hence this paper focuses on the computer scientists perspective, it is important to look at the implications on digital security, especially cryptography.
 
@@
 This effect is called superposition. To put qubits into superposition, 
-researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and has to obey to the same laws, 
-a measurement determines the state. Once qubits are measured, 
-it's quantum state immediately collapses to either 1 or 0.
+researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and hence has to obey to the same laws, 
+a measurement determines the state of a qubit. Once qubits are measured, 
+it's quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.
 
-Entanglement causes pairs of qubits to entangle.
+Quantum entanglement is a phenomenon which causes particles to link so that their state cannot be described independently anymore.
 This results in those entangled qubits having a similar quantum state at all times.
@@
 the other one will instantaneously change its state as well.
-This improved the processing speed of quantum computers.
+This improves the processing speed of quantum computers.
 As Alamira Jouman Hajjar puts it in her Article on AIMultiple \cite{AIMultiple}, one qubit will reveal information about all the qubits said qubit is entangled with.
-This entanglement allows quantum computers to increase it's computational power exponentially,
+This entanglement allows quantum computers to increase its computational power exponentially,
 rather than linearly on regular computers.
@@
 
-Qubits quantum behavious is determined to decay.
+The quantum behaviour of qubits is determined to decay.
 This effect is known as the scientific term "decoherence".
 It describes the quantum state as being extremely fragile.
-The slightest disturbance can cause a qubit to loose its state of superposition.
-These disturbances can be created by vibrations, change of temperatures or related external influeces.
+The slightest disturbance can cause a qubit to collapse and hence loose its state of superposition.
+These disturbances can be caused by vibrations, change of temperatures or related external influeces.
 Disturbances are also refered to as "noise" in quantum computer terminology.
-This is the reason why qubits and quantum computers are held in extremly protected environments, 
+Decoherence is the reason why qubits quantum computers are held in extremly protected environments, 
 often fridges or vacuum chambers.
@@
 refered to as a "logical" qubit. 
-To set this into context, 
+A logical qubit has a long enough coherence time to be used for quantum logic gates. 
+Essentially, logical qubits are a group of regular qubits refered to as a singular qubit in computation, 
+which have more stable characteristics than regular qubits.
+
+To get a sense of how far development of quantum computers has come, 
 according to Siobhan Roberts in MIT Technology Review \cite{MIT}, 
 the most qubits used in a quantum computer, 
-as of November 17, 2021 are 256 in a quantum computer by the Boston startup QuEra Computing. 
+as of November 17, 2021 are 256 regular qubits in a quantum computer by the Boston startup QuEra Computing.
+
+Since the first proposals revolving around quantum computers by Yuri Manin in 1980 and Richard Feynman in 1981,
+the term "quantum supremacy" is used to denote the point at which a quantum computer can complete a mathematic calculation that is beyond reach of even the most powerful supercomputers.
+It is unclear how many qubits will be needed to achieve superposition. 
+This results out of the fact that research results in new algorihtms and hardware improvements to boost the performance of classical (super)computers.
+
+Potential applications for quantum computer exceed cryptography.
+Some potential applications include the simulation of quantum systems, machine learning, computational biology and generative chemistry.
+
 There is not a single way to build a quantum computer. 
-Instead, different approaches can be followed to develop machines utilizing quantum effects for computing.
-
-Since the first proposals revolving around quantum computers back in 1980 by Yuri Manin and Richard Feynman in 1981,
-the term "quantum supremacy" is used to denote the point at which a quantum computer can complete a mathematic calculation that is beyond reach of even the most powerful supercomputer.
-It is unclear how many qubits will be needed to achieve this because researchers keep finding new algorihtms to boost the performance of classical computers and supercomputing hardware is getting better as well.
+Instead, different approaches can be followed to develop machines utilizing quantum effects for computing. Some of which will be discussed in the following section.
 
@@
     Direct inspection for errors should be avoided as it will cause the value to collapse, leaving it superposition state.
-    % Citation below
     \item The difficulty of coherence is another challenge. 
@@
 
-% Add maths of Shor and Grover
 \begin{section}{Quantum computing algorithms and their effects on current security mechanisms}
@@
 \begin{subsection}{Shor's algorithm}
-% Think about talking about quantum gates
 Shor's algorithm is a polynomial-time quantum computer algorithm for integer factorization.
@@
 If a quantum computer with a sufficient number of qubits could operate without succumbing to quantum noise and other quantum-decoherence phenomena, 
-% Cite Kirsch here
 Shor's algorithm could be used to break public-key cryptography schemes, 
@@
 
-% Maybe refer to the first nmr attempt of 2001. Access to the paper is given.
 So far, the largest number factorized using Shor's algorithm, 
@@
 Grover's algorithm can be utilized to find a collision in a hash function in $O(sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
-% TODO: Cite brassard
-Additionally, it has been proved that it is possible to combine Grover's algorithm with the birthday paradox, 
-also known as a quantum birthday attack. 
+Brassard proved \cite{1998} that it is possible to combine Grover's algorithm with the birthday paradox, 
+also known as a quantum birthday attack, which makes Grover's algorithm even more efficient. 
 As a result, many of the present hash alogithms are disqualified for use in the quantum era. 
@@
 
-% Research for this paragraph in a second paper
+% Research for this paragraph and add some more post quantum crypto examples
 \begin{section}{Post Quantum Cryptography}
@@
 \end{section}
-% Conclusion: I see it as an improvement, not as dangerous
 
@@
 since way more qubits are needed to perform operations on large enough numbers and preserve the state of superposition long enough. 
+To conclude, it should be said that quantum computing should be seen as an opportunity for overdue improvement, not as a thread to digital security. 
 \end{section}

### 2021-12-12 paper.tex
feat: Improve ion trap

@@
 Instead, different approaches can be followed to develop machines utilizing quantum effects for computing. Some of which will be discussed in the following section.
-
 \end{section}
@@
 
-There are different attempts of realizations of quantum computers.
+There are different approaches to realize quantum computers.
 Those different approaches have different advantantages and challenges. 
@@
 \begin{subsection}{Ion Traps}
-The ion trap quantum computer encodes data in energy states of ions and in vibrational modes between ions. 
-Conceptually, each ion is operated by a sepearte laser. 
-A preliminary analysis demonstrated that Fourier transforms can be evaluated with the ion trap computer. 
-This, in turn, leads to Shor's factoring algorithm, 
-which is based on Fourier transforms.
+Vedral and Plenio describe the workings of the ion trap in their paper \cite{2008} as follows. 
+They state that the ion trap quantum computer represents qubits in energy states and in vibrational modes between ions. 
+In a linear ion trap, currents in electrodes generate a time dependent electric field. 
+Ions then move through this potential and for some currents and ion masses, the ions get trapped in the field. 
+The equilibrium is caused by the force from the electric field generated by the electrodes and the electrostatic repulsion of the ions. 
+The ions form a string seperated by only a few wavelengths of light. 
+The distance of a few wavelengths is sufficient to operate each ion with a different laser. 
+A challenge the researchers faced when trying to realize an ion trap is the mechanical degree of freedom the ions have. 
+In general, the ions are trapped at their position but they are in fact not resting but oscillating around their equilibrium position. 
+The ions then get cooled by using laser cooling to reduce the movement of the ions in their current position. 
+This process is able to cool down the ions near 0 Kelvin. 
+At this point, the only movement left would be the movement caused by the quantum mechanical uncertainty priciple. 
+So far, it is not possible to cool a whole string of ions to near 0 K, 
+although several attempts cooling down a single ion and two ions succeeded.
 
-Also refered to as "trapped ion quantum computer". 
-The fundamental operations of a quantum computer have been demonstrated experimentally with the currently highest accuracy in trapped ion systems. 
-Trapped ion computers are researched because they could be used for a large-scale quantum computer.
-Scaling the ion trap to a large number of qubits could be accomplished by combining multiple ion traps into an array and transporting ions between them. 
+As mentioned by Prashant in his paper \cite{prashant}, it has been possible to evaluate Fourier transforms using the ion trap quantum computer.
+This achievment lead to Shor's factoring algorithm, 
+which is based on performing Fourier transforms.
+
+The ion trap could demonstrate the fundamental operations of a quantum computer with the highest accuracy so far. 
+Ion trap quantum computers are researched because they could potentially be used for a large-scale quantum computer as scaling the ion trap to a large number of qubits could be accomplished by combining multiple ion traps into an array.
+Ions then could be transported between the ions traps.
 As of 2018, the largest number of particles to be controllable entangled is 20 trapped ions. 
-In 2021, researchers from the University of Innsbruck presented a quantum computing demonstrator that fits inside two 19-inch server racks, 
-the world's first qualirt standards meeting compact trapped ion quantum computer.
-
-Challenges for ion traps include initialization of the ion's motional states, 
-the relatively brief lifetimes of the photon states and the decoherence which is is caused when the qubits interact with the external environment undesirably.
+In 2021, scientists from the University of Innsbruck presented a quantum computer based on the ion trap that fits inside two 19-inch server racks.
 \end{subsection}

### 2021-12-12 paper.tex
feat: Improve nuclear magnetic resonance

@@
 \usepackage{url}
-
-% Add page numbers to papers
-% Where I make references, put actual hyperlinks
 
@@
 This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
-Hence this paper focuses on the computer scientists perspective, it is important to look at the implications on digital security, especially cryptography.
+Hence it is important to look at the implications on digital security, especially cryptography.
 
@@
 a measurement determines the state of a qubit. Once qubits are measured, 
-it's quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.
+its quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.
 
@@
 \begin{subsection}{Nuclear Magnetic Resonance}
-A Nuclear Magnetic Resonance (NMR) computer consists of a capsule filled with a liquid and an NRM machine. 
-Each molecule in the liquid is an independet quantum memory register. 
-Computation proceeds by sending radio pulses to the sample and reading its response. 
-Qubits are implemented as spin states of the nuclei of atoms comprising the molecules. 
-In contrast to the Ion Trap computer, 
+As explained in the article by Gershenfeld \cite{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
+Each molecule in the liquid represents an quantum memory register. 
+NMRs can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
+In an NMR quantum computer, qubits are represented as spin states of the atoms in the molecules. 
+In contrast to the ion trap quantum computer, 
 a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register.
-NMR computers have been achieving the most accomplishements in quantum computing so far, 
-as they can solve non-polynomial complete problems in a polynomial time.
 
-Initially the approach was to use the soin properties of atoms of particular molecules in a liquid sample as qubits - 
-this is known as liquid state NMR (LSNMR). 
-This approach has since been superseeded by solid state NRM (SSNMR) as a means of quantum computation.
+Initially, as mentioned above, the NMRs used atoms in a liquid sample as qubits which is known as liquid state NMR (LSNMR). 
+Since solid state NMRs (SSNMR) emerged, SSNMR is usually preferred in terms of performing quantum computation.
 
-Solid state NMR (SSSNMR) differs from LSNMR in that we have a solid state sample, 
-for example a nitrogen vacancy diamond lattice rather than a liquid sample. 
-This has many advantages such as lack of molecular diffusion coherence, 
-lower temperatures can be achieved to the point of suppressing phonon decoherence and a greater variety of control operations that allow us to overcome one of the major problems of LSNMR that is initialisation.
-Moreover, as in a crystal structure we can localize precisely the qubits, 
-we can measure each qubit individually, 
-instead of having an ensemble measurement as in LSNMR.
+Solid state NMR (SSSNMR) differ from LSNMR in that SSSNMR provide a solid state sample.
+This has many advantages such as lack of molecular diffusion coherence and lower temperatures, as well as the more precise localization of qubits using crystal structures.
+In SSNMRs, qubits can be measured individually, same as in the ion trap,
+instead of having to measure an ensemble of molecules as in LSNMR.
 
-More recent work shows that all experiments in liquid state bulk ensemble NMR quantum computing to date do not possess quantum entanglement, 
-thought to be required for quantum computation. 
-Hence NMR quantum computing experiments are likely to have been only classical simulations of a quantum computer. 
+NMRs have been succesfully used in quantum computing, as they can solve non-polynomial problems in a polynomial time.
+According to Gershenfeld \cite{Gershenfeld1998QuantumCW}, the first successful computation on a NMR quantum computer was to execute a search using Grover's algorithm, 
+which will be covered in the respective chapter. 
 \end{subsection}

### 2021-12-12 paper.tex
feat: Improve Josephson junctions

@@
 
-\begin{subsection}{Josephson Junctions}
-A Josepson junction quantum computer is a Cooper pair box,
-which is a small superconducting island electrode weakly coupled to a bulk superconductor. 
-In literature, the Josephson junctions are also refered to as superconducting quantum computers.
-Weak coupling between the superconductors create a Josephson junction between them which behaves as a capactor. 
-If the Cooper box is as small as a quantum dot, 
-the charging current breaks into discrete transfer of individual Cooper pairs. 
-Ultimately, it is possible to just transfer a single Cooper pair across a junction. 
+\begin{subsection}{Josephson Junction}
+As Martinis and Osborne explain in their paper, 
+the Josephson effect is a phenomenon that occurs when two superconductors are seperated 
+by some barrier or restriction between them, which is thin enough that electrons can tunnel through the barrier using quantum-mechanics. 
+This tunneling produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
+This is used to create a non-linear inductance and design the qubits. 
+Wendin and Shumeiko mention \cite{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
+The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
+The josephson energy comes from kinetic energy of the tunneling electrons.
+
+Martinis and Osborne state that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.
+
 Qubits in Josephson junction quantum computers are controlled electrically which results in them being interesting for future developments.
-
-In Physics, the Josephson effect is a phenomenon that occurs when two superconductors are placed in proximity, 
-with some barrier or restriction between them. 
-The Josephon effect produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
-This current thorught the junction occurs by quantum tunneling. 
-This is used to create a non-linear inductance which is essential for qubit design, 
-as it allows a design of anharmonic oscialltors. 
-A quantum harmonic oscillator cannot be used as a qubit, 
-as there is no way to address only two of its states. 
 \end{subsection}

### 2021-12-12 paper.tex
feat: Add martinis citation

@@
 
-Martinis and Osborne state that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.
+Martinis and Osborne state \cite{martinis} that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.
 

### 2021-12-13 paper.tex
feat: Improve Challgenes in Quantum Computing

@@
 
-\begin{subsection}{Josephson Junction}
+\begin{subsection}{Josephson Junctions}
 As Martinis and Osborne explain in their paper, 
@@
 \begin{section}{Challenges in Quantum Computing}
-As of 2021, there are some challenges in quantum computing researchers are working on:
+As of 2021, there are some challenges researcher in the current state of quantum computing which can be derived from the earlier chapters:
 
 \begin{itemize}
-    \item Quantum algorithms are mainly probabilistic. 
-    This means that in one opeartion a quantum computer returns many solutions where only one is correct. 
-    This trial and error for measuring and verifying the correct answer weakens the advantage of quantum computing speed. 
-    \item Qubits are susceptible to errors earlier introduced as noise. 
-    They can be affected by heat, noise in the environment, 
-    as well as stray electromagnetic couplings. 
-    Classical computers are susceptible to bit-flips. Qubits suffer form said bit-flips as well as phase errors. 
-    Direct inspection for errors should be avoided as it will cause the value to collapse, leaving it superposition state.
-    \item The difficulty of coherence is another challenge. 
-    Qubits can retain their quantum state only for a short period of time. 
+    \item Often, as e.g.
+in the Josephson junction quantum computer, extremely low temperatures are needed.
+These have to be achieved at reasonable cost.
+Using e.g.
+laser cooling is a one approach in quantum computing.
+The concept of laser cooling was proposed by Steven Chu, Claude-Cohen-Tannoudji and William D.
+Phillips who got awarded the Nobel prize for their research in the develoment of methods to cool and trap atoms with laser light.
+    \item Quantum algorithms have probabilistic characteritics. 
+    This implies that in a single operation a quantum computer returns multiple solutions, each of those solutions with an assigned probability, where only one can be correct. 
+    Figuring out the correct answer reduces the potential speed of quantum computers.
+    \item Qubits are prone to errors earlier introduced as noise. 
+    Noise can be caused e.g. by heat or noise in the environment. 
+    As in classical computing, this noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
+    One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
+    \item Increasing the number of qubits in a processor.
+The more qubits in a processor, the more logical qubits can be used.
+More qubits also lead to less errors since methods for error correction can be used more effectively.
+    \item Decoherence leads to qubits retaining their quantum state only for a short period of time. 
     According to Mavroeidis \cite{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
@@
 This implies that the quantum computer could also solve problems which a regular computer could not solve so far.
-Which problems can be solved and which security mechanisms are affected will be discussed in this following section.
+Some of the problems that can be solved and which security mechanisms are affected will be discussed in this following section.
 

### 2021-12-13 paper.tex
feat: Improve Shor's algorithm

@@
 
-% Look into paper for this. The paper has a perfect level for our own research.
 \begin{subsection}{Shor's algorithm}
-Shor's algorithm is a polynomial-time quantum computer algorithm for integer factorization.
-Essentially it solves the following problem: 
-Given an integer $N$m find its prime factors. 
-On a quantum computer, to factor an integer $N$, 
-Shor's algorithm runs in polynomial time. 
-Using quantum gates demonstrates, 
-that integer-factorization can be solved on a quantum computer an is consequently in the complexity class BQP, 
-which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $1/3$ for all instances. 
-This algorithm is almost exponentially faster than the most efficient known classical factoring algorithm, the general number field sieve which is the most efficient known factoring algorithm on regular computers.
-The efficiency of Shor's algorithm is due to the efficiency of the quantum Fourier transform and modular exponentiation by repeated squearings. 
-If a quantum computer with a sufficient number of qubits could operate without succumbing to quantum noise and other quantum-decoherence phenomena, 
-Shor's algorithm could be used to break public-key cryptography schemes, 
-such as the RSA scheme or the Diffie-Hellman key exchange. That these algorithms could be vulnerable was already stated by Kirsch in 2015
+Shor's algorithm is a quantum computer algorithm and got developed by Peter Shor in 1994.
+Essentially, it can find the prime factors of an integer in the complexity class BQP,
+which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $\frac{1}{3}$ for all instances. 
+Shor's algorithm is nearly exponentially faster than the general number field sieve, which is the most efficient known classical factoring algorithm.
+The efficiency of the quantum Fourier transform which, as earlier discussed, can be caluclated using e.g. an ion trap quantum computer, is responsible for the efficiency of Shor's algorithm.
+The algorithm is generally capable to break current public-key cryptography mechanisms as RSA or the Diffie-Hellman key exchange if the quantum computer could operate with little noise. 
+That these algorithms could be vulnerable was already stated by Kirsch in 2015
 \cite{Kirsch2015QuantumCT}.
+
+Bone and Castro \cite{Bone} describe the workings of Shor's algorithm as follows.
+First, a memory register is placed into a superposition of all its possible states.
+Think of all possible permutations of $n$ bits existing in parallel.
+A calculation performed with Shor's algorithm can be thought of as computations done in parallel for every of the permutations generated before. 
+They then describe the mathematics performed on the registers: 
+\begin{itemize} 
+    \item N describes the integer to be factorized
+    \item X is a random number in range $1 < X < N-1$
+    \item X is raised to one of the permutations generated earlier.
+    \item The remainder of this operation is placed in a second register. The first register contains the permutation.
+\end{itemize}
+After performing these operations on all permutations, it is noticable that the contents of the second register repeat e.g. for $N = 15$ the repeating sequence would be $1,2,4,8,1,2,4...$.
+Now the frequency of repetition can be calculated by using a complex operation on the second register and the looking at the contents which causes the results from every permutation to interfere.
+A possible prime factor can then be calculated by using the frequency of repetition $f$:
+\begin{equation}
+Factor P = X^{\frac{f}{2}}-1
+\end{equation}
+The inteference that provides $f$ will lead to the correct answer with a high probability as incorrect answers cancel each other out when interfering.
+This cannot be guaranteed!
+Checking that the resulting number is correct can be achieved by performing a simple multiplication.
+Repeating the process for different random values X has then a high chance of revealing all prime factors.
 
@@
 but the algorithm failed. 
-
-% Eventually add math for Shor's algorithm
 \end{subsection}

### 2021-12-13 paper.tex
feat: Improve Grover's algorithm

@@
 
-% Consider paper for this section as well
 \begin{subsection}{Grover's algorithm}
-% Think about writing either 128 bit or 128-bit in the whole paper
 Grover's algorithm, devised by Lov Grover in 1996,
 refers to a quantum algorithm for performing unstructered search. 
-The analogous problem in classical computing cannot be solved in fewer than $O(N)$ evaluations. 
+The analogous problem in classical computing has $O(N)$ complexity. 
 Grover's algorithm is achieving the same goal in $O(\sqrt{N})$. 
@@
 Grover's algorithm only provides quadratic speedup.
-Considering Grover's algorithm could be used to brute-force a 128-biy symmetric key in roughly $2^{64}$ iterations, 
-or a 256-bit key in roughly $2^{128}$ iterations.
 
-Grover's algorithm can be utilized to find a collision in a hash function in $O(sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
+As \cite{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
+Additionally, Grover's algorithm can be used to improve a lot of brute-force attacks targeting symmetric cryptography.
 Brassard proved \cite{1998} that it is possible to combine Grover's algorithm with the birthday paradox, 
-also known as a quantum birthday attack, which makes Grover's algorithm even more efficient. 
-As a result, many of the present hash alogithms are disqualified for use in the quantum era. 
-However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant.
+also known as a quantum birthday attack, which leads to finding collisions with a complexity of $O(N^{\frac{1}{3}})$.
+As a result, many of current , rather weak, hashing alogithms are disqualified for use in the quantum era. 
+However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant as even Grover's algorithm does not make it feasible to to find a collision when the keys are too long.
 \end{subsection}
@@
 \begin{section}{Post Quantum Cryptography}
-Additionally, it will be discussed what defines a quantum-proof algorithm. 
 Post Quantum Cryptography descrbes algorithms that are secure against quantum computing and against conventional computers.

### 2021-12-13 paper.tex
feat: Improve post quantum security and conslusion

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Donec in ex ut mauris mollis dictum.
-Aenean tempor scelerisque lectus, eu varius ex ullamcorper ac.
-Nulla quis mattis tellus.
-Vivamus imperdiet ante sit amet tellus dapibus imperdiet.
-Quisque iaculis consequat cursus.
-Morbi in tempor neque, eu aliquet est.
-Pellentesque dapibus nulla id sem scelerisque eleifend.
-Ut tincidunt ex nec erat pharetra pretium.
-Vivamus bibendum quam id nunc fermentum tincidunt.
-Duis congue semper nulla sed porttitor.
-Morbi feugiat suscipit pellentesque.
-Nullam eget velit vel ligula suscipit convallis.
+Quantum computing has been gaining more and more relevance in the last couple of years and is often rather seen as a thread than a blessing by society.
+This paper aims to inform readers about the topic on a high-level to join the discussion about the future relevance of quantum computing.
+First, this paper will explain the basics of quantum computing and dive into types of quantum computers including ion traps, nuclear magnetic resonance quantum computers and quantum computers based on josephson junctions.
+Afterwards, the effects of quantum computing algorithms, especially Shor's and Grover's algorithm on current security mechanisms are discussed, rounding off by explaining approaches on how to achieve post quantum security.
 \end{abstract}
@@
 \begin{section}{Post Quantum Cryptography}
-Post Quantum Cryptography descrbes algorithms that are secure against quantum computing and against conventional computers.
-Increasing the key size from e.g. 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm.
-The goal is the same as it was before quantum computers ermerged.
-The operations to crack the security mechanisms have to become infeasable to perform.
+Post Quantum Cryptography describes algorithms that are secure against quantum computing and conventional computers.
+To make sure that an algorithm is quantum secure, there are generally two approaches:
 
+\begin{subsection}{Improve Current Security Mechanisms}
+Improving current security mechanisms by increasing the key length from 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search unsing Grover's algorithm. 
+The speedup Grover's algorithm provdides is not that efficient as that it could crack this key in a feasible amount of time.
+\end{subsection}
+
+\begin{subsection}{Developing Quantum Secure Algorithms}
 Another approach would be to develop new algorithms using more complex trapdoor functions even quantum computers could not possibly crack in a feasible amount of time. 
-Researchers are working in areas like lattice-based cryptography and supersingular isogeny key exchange.
+Researchers are working in areas like lattice-based cryptography, supersingular isogeny key exchange or hash-based cryptography. One of these approaches will be described in the following:
 
-\begin{subsection}{Lattice-based Cryptography}
-This is a form of public-key cryptography that avoids the weaknesses of RSA. 
+\begin{subsubsection}{Lattice-based Cryptography}
+Lattice-based Cryptography is a form of public-key cryptography that avoids the weaknesses of RSA and related security mechanisms. 
 Rather than multiplying primes, lattice-based encryption schemes involve multiplying matrices. 
-Furthermore, lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems. 
-Here, we are given as input a lattice represented by an aribtrary basis and our goal is to output the shortest non-zero vector in it.
+As Micciancio and Regev mention in their paper \cite{Micciancio2009}, 
+lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems and it is belived that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,
+which is used in Shor's algorithm cannot be used in lattice-based problems. 
+\end{subsubsection}
+
 \end{subsection}
@@
 as well as Grover's algorithm will presumably force computer scientists to improve current stadards to provide information security across areas. 
-To accomplish information security, 
-current security mechanisms such as hashing algorithms have to be improved and as a result be quantum-safe by increasing their key-length.
 The second approach mentioned in this paper is developing new, 
@@
 It has to be said that quantum computers, 
-as what could be seen in the current records revolving around quantum computing, 
+as what could be seen in current records,  
 are not powerful enough to form a thread to security mechanisms by now, 

### 2021-12-14 paper.tex
feat: Add page numbers to citations

@@
 \begin{subsection}{Ion Traps}
-Vedral and Plenio describe the workings of the ion trap in their paper \cite{2008} as follows. 
+Vedral and Plenio describe the workings of the ion trap in their paper \cite[p.12-13]{2008} as follows. 
 They state that the ion trap quantum computer represents qubits in energy states and in vibrational modes between ions. 
@@
 At this point, the only movement left would be the movement caused by the quantum mechanical uncertainty priciple. 
-So far, it is not possible to cool a whole string of ions to near 0 K, 
+So far, it is not possible to cool a whole string of ions to near 0 Kelvin, 
 although several attempts cooling down a single ion and two ions succeeded.
 
-As mentioned by Prashant in his paper \cite{prashant}, it has been possible to evaluate Fourier transforms using the ion trap quantum computer.
+As mentioned by Prashant in his paper \cite[p.20]{prashant}, it has been possible to evaluate Fourier transforms using the ion trap quantum computer.
 This achievment lead to Shor's factoring algorithm, 
@@
 \begin{subsection}{Nuclear Magnetic Resonance}
-As explained in the article by Gershenfeld \cite{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
+As explained in the article by Gershenfeld \cite[p.66-71]{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
 Each molecule in the liquid represents an quantum memory register. 
@@
 NMRs have been succesfully used in quantum computing, as they can solve non-polynomial problems in a polynomial time.
-According to Gershenfeld \cite{Gershenfeld1998QuantumCW}, the first successful computation on a NMR quantum computer was to execute a search using Grover's algorithm, 
+According to Gershenfeld \cite[p.69]{Gershenfeld1998QuantumCW}, the first successful computation on a NMR quantum computer was to execute a search using Grover's algorithm, 
 which will be covered in the respective chapter. 
@@
 This is used to create a non-linear inductance and design the qubits. 
-Wendin and Shumeiko mention \cite{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
+Wendin and Shumeiko mention \cite[p.727]{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
 The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
@@
 
-Martinis and Osborne state \cite{martinis} that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.
+Martinis and Osborne state \cite[p.3]{martinis} that Josephson junction quantum computers are especially interesting because superconductors could provide long coherence times and because increasing the number of qubits should be straightforward.
 
@@
     \item Decoherence leads to qubits retaining their quantum state only for a short period of time. 
-    According to Mavroeidis \cite{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
+    According to Mavroeidis \cite[p.3]{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales.
     Their qubits remained in superposition for a total of 35 seconds.
@@
 That these algorithms could be vulnerable was already stated by Kirsch in 2015
-\cite{Kirsch2015QuantumCT}.
+\cite[p.6]{Kirsch2015QuantumCT}.
 
-Bone and Castro \cite{Bone} describe the workings of Shor's algorithm as follows.
+Bone and Castro \cite[p.6-9]{Bone} describe the workings of Shor's algorithm as follows.
 First, a memory register is placed into a superposition of all its possible states.
@@
 
-As \cite{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
+As Mavroeidis et al \cite[p.4]{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
 Additionally, Grover's algorithm can be used to improve a lot of brute-force attacks targeting symmetric cryptography.
@@
 Rather than multiplying primes, lattice-based encryption schemes involve multiplying matrices. 
-As Micciancio and Regev mention in their paper \cite{Micciancio2009}, 
+As Micciancio and Regev mention in their paper \cite[p.2]{Micciancio2009}, 
 lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems and it is belived that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,

### 2021-12-16 paper.tex
fix: Typo

@@
 \begin{abstract}
-Quantum computing has been gaining more and more relevance in the last couple of years and is often rather seen as a thread than a blessing by society.
+Quantum computing has been gaining more and more relevance in the last couple of years and is often rather seen as a threat than a blessing by society.
 This paper aims to inform readers about the topic on a high-level to join the discussion about the future relevance of quantum computing.

### 2021-12-26 paper.tex
fix: Typos

@@
 quantum computing has become a large research area. 
-Even so large, that is has become more and more difficult to understand the basics of it and its implications on the future of computing. 
+Even so large, that it has become more and more difficult to understand the basics of it and its implications on the future of computing. 
 This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
@@
 It describes the quantum state as being extremely fragile.
-The slightest disturbance can cause a qubit to collapse and hence loose its state of superposition.
-These disturbances can be caused by vibrations, change of temperatures or related external influeces.
+The slightest disturbance can cause a qubit to collapse and hence lose its state of superposition.
+These disturbances can be caused by vibrations, change of temperatures or related external influences.
 Disturbances are also refered to as "noise" in quantum computer terminology.
@@
 \begin{subsection}{Nuclear Magnetic Resonance}
-As explained in the article by Gershenfeld \cite[p.66-71]{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
+As explained in the article by Gershenfeld \cite[p.66-71]{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and a nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
 Each molecule in the liquid represents an quantum memory register. 
@@
 Phillips who got awarded the Nobel prize for their research in the develoment of methods to cool and trap atoms with laser light.
-    \item Quantum algorithms have probabilistic characteritics. 
+    \item Quantum algorithms have probabilistic characteristics. 
     This implies that in a single operation a quantum computer returns multiple solutions, each of those solutions with an assigned probability, where only one can be correct. 
@@
 As described before, Shor's algorithm, 
-as well as Grover's algorithm will presumably force computer scientists to improve current stadards to provide information security across areas. 
+as well as Grover's algorithm will presumably force computer scientists to improve current standards to provide information security across areas. 
 The second approach mentioned in this paper is developing new, 

### 2021-12-31 paper.tex
feat: Add related work, fix author names in citations

@@
 Hence it is important to look at the implications on digital security, especially cryptography.
+
+\end{section}
+
+\begin{section}{Related Work}
+There are already several papers about the functionality of quantum computers and quantum algorithms. 
+However, finding a comprehensive overview turned out to be hard.
+
+Prashant writes about the limitations of classical computers and how quantum computers can be realized \cite{prashant}. 
+Their brief explanations on different realizations of quantum computers are introducing the reader to several research areas on a high level.
+
+Providing detailed examples of the workings of Shor's and Grover's algorithm are Bone and Castro in their overview of quantum computing \cite{Bone}.
+
+Vedral and Planio provide an especially interesting and detailed explanation of ion trap quantum computers in their paper \cite{2008}.
+
+Martinis and Osborne write about josepshon junctions \cite{martinis} and how the josephson effect can be used to create a quantum computer utilizing superconductors.
+
+Diving a little bit deeper, Mavroeidis et al.
+introduce the reader to present cryptography algorithms, how they are vulnerable to quantum computers and about their main topic, post quantum security \cite{DBLP:journals/corr/abs-1804-00200}.
+
+The largest number factorized on a quantum computer so far using Shor's algorithm was the number 21. Martìn-Lòpez et al. write about how they achieved this breakthrough in their paper \cite{article}.
+
+Micciancio and Regev introduce the topic of lattice-based cryptography \cite{Micciancio2009}, which is believed to be a post-quantum secure method by multiplying matrices instead of primes.
 
@@
 \begin{subsection}{Josephson Junctions}
-As Martinis and Osborne explain in their paper, 
+As Martinis and Osborne explain in their paper \cite[p.3-6]{martinis}, 
 the Josephson effect is a phenomenon that occurs when two superconductors are seperated 
@@
 
-So far, the largest number factorized using Shor's algorithm, 
-as of 2019 is the number 21 factored back in 2012 by Martín-López et al \cite{article}. 
+So far, the largest number factorized using Shor's algorithm 
+ is the number 21 factored back in 2012 by Martín-López et al. \cite{article}. 
 The integer 35 was attempted in 2019 on an IBM Q System One, 
@@
 
-As Mavroeidis et al \cite[p.4]{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
+As Mavroeidis et al.
+\cite[p.4]{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search.
 Additionally, Grover's algorithm can be used to improve a lot of brute-force attacks targeting symmetric cryptography.
@@
 To make sure that an algorithm is quantum secure, there are generally two approaches:
-
 \begin{subsection}{Improve Current Security Mechanisms}    

### 2022-01-02 lerntagebuch.tex
feat: Work on Lerntagebuch

@@
 \maketitle 
+Dieses Lerntagebuch wird unter anderem auch dazu genutzt, mich vor dem schreiben aufzuwärmen.
 
-Ich werde dieses Lerntagebuch unter anderem auch dazu nutzen, mich vor dem schreiben aufzuwärmen. 
 Ich habe mich dazu entschieden das Paper iterativ zu schreiben.
-Ich schreibe um das Thema selber zu verstehen ein erstes Konzept mit erklärungen der verschiedenen Themen die relevant erscheinen.
+Ich schreibe um das Thema selber zu verstehen ein erstes Konzept mit erklärungen der verschiedenen Themen, welche relevant erscheinen.
 In der zweiten Iteration erstelle ich eine koherentere Version des bisherigen Inhalts und in der letzten Iteration überarbeite ich den Inhalt und die Formulierungen.
 Die Latex-Einführung half mir dabei, Latex lieben zu lernen.
-Ich verwendete Latex häufig zuvor ohne wirklich zu wissen, was dahinter steckt und was ich tue.
-Seit der Einführung habe ich mich kontinuierlich weiter mit Latex beschäftigt bis ich zu dem Punkt gelangt bin, sogar meine Präsentation mit Hilfe von der Latex-Documentclass "beamer" zu erstellen.
-Ich habe mich dazu entschieden, die "revtex4" documentclass für mein Paper zu verwenden.
+Ich verwendete Latex häufig für Dokumentation ohne wirklich zu wissen, was dahinter steckt und was ich tue.
+Seit der Einführung habe ich mich kontinuierlich weiter mit Latex beschäftigt bis ich zu dem Punkt gelangt bin, sogar meine Präsentation mit Hilfe der Latex-Documentclass "beamer" zu erstellen.
+
+In meinem Paper wird die "revtex4" documentclass verwendet.
 Es ist ein Standard aus der Physik, welcher mich auch schon in vielen anderen Themengebieten aufgefallen ist.
 Durch diesen Standard ist das Paper zwar nur die hälfte der Seiten lang, sieht aber dafür so aus, wie ich mir ein Paper immer vorgestellt habe.
-Ich frage mich häufig, welches Wissen ich zitieren muss und was ich einfach so niederschreiben darf, da es keine Intellektuelle höhe benötigt hat, um diese Dinge festzustellen.
 
+Ich frage mich häufig, welches Wissen ich zitieren muss und was ich einfach so niederschreiben darf, da es keine intellektuelle Höhe benötigt hat, um diese Dinge festzustellen oder abzuleiten.
+Allgemeinwissen muss zwar nicht zitiert werden, aber das Allgmeinwissen ist abhängig vom Stand des Lesers.
+Wird ein Paper von Physiker*innen an Physiker*innen geschrieben, kann man ein anderes Allgemeinwissen vorraussetzen, als wenn Ökonom*innen an andere Ökonom*innen schreiben.
+Dies hat es für mich oft schwer gemacht, festzustellen, was gerade zu "meinem" Allgemeinwissen gehört und was nicht.
+
+Der Rechercheprozess verlief genauso wie in der Vorlesung angekündigt.
+Nachdem man einführende Paper gelesen hat, vertieft man sich weiter mit weiteren Papers zu Themen, die im ersteren Paper nicht ausreichend behandelt wurden.
+Dieser Prozess hat sich dann so oft wiederholt, bis genug Wissen akkumulliert wurde, um das Paper zu verfassen.
+In meinem Fall ist das zum Beispiel bei "Shor's Algorithm" oder den "Josephson Junctions" aufgetreten.
+Für das Paper habe ich ausschließlich englische Literaturquellen verwendet, da auch das Paper auf Englisch ist.
+
+Während des Schreibprozesses habe ich eine Vorstellung dessen erlangt, was es heißen muss wirkliche Erkenntnisse vorbringen zu müssen.
+Ich würde Behaupten das Thema "Quantencomputer" nur angekratzt zu haben.
+Eine Person, die tatsächlich Erkenntnisse hervorbringen soll, muss unfassbar viel mehr Arbeiten lesen und verstehen als ich das im Rahmen dieser Arbeit tun musste, um auf den aktuellen Stand der Technik zu kommen und diesen zu verstehen.
+Daraus dann noch neue Erkenntnisse abzuleiten, lässt nachvollziehen, warum eine Doktorarbeit in der Regel mehrere Jahre dauert.
+
+Sehr schwer gefallen ist mir die "Related Work" section.
+Diese kann meiner Meinung nach erst am Ende geschrieben werden, da die Struktur des Papers dann auch in die Struktur dieses Abschnittes einfließen kann.
+Außerdem ist es mir schwergefallen festzustellen, ob die Related Work section die Erkenntnisse enthalten soll, die für mein Paper wichtig waren oder ob eine generelle Zusammenfassung des Papers erwartet wird.
+Ich hoffe, dass ich diesen Abschnitt in zukünftigen Papers noch verbessern kann.
+
+Ein witziger Seiteneffekt dieses Papers ist, dass ich erfahren habe, dass einer der im Paper erwähnten Quantencomputer in Böblingen bei IBM steht, bei welchen in im kommenden Semester mein Praxissemester absolvieren werde.
+Ich werde mich informieren, ob eine Besichtigung dessen möglich ist.
 \end{document}

### 2022-01-05 paper.tex
fix: Related work
feat: Finish paper

@@
 \begin{abstract}
-Quantum computing has been gaining more and more relevance in the last couple of years and is often rather seen as a threat than a blessing by society.
-This paper aims to inform readers about the topic on a high-level to join the discussion about the future relevance of quantum computing.
+Quantum computing has been gaining more and more relevance in recent times and is often rather seen as a threat than a blessing by society.
+This paper aims to inform readers about the topic on a high-level to be able to join the discussion about the future relevance of quantum computing.
 First, this paper will explain the basics of quantum computing and dive into types of quantum computers including ion traps, nuclear magnetic resonance quantum computers and quantum computers based on josephson junctions.
@@
 \begin{section}{Related Work}
-There are already several papers about the functionality of quantum computers and quantum algorithms. 
-However, finding a comprehensive overview turned out to be hard.
-
 Prashant writes about the limitations of classical computers and how quantum computers can be realized \cite{prashant}. 
-Their brief explanations on different realizations of quantum computers are introducing the reader to several research areas on a high level.
+Their brief explanations on different realizations of quantum computers is introducing the reader to several related research areas on a high level.
 
@@
 Diving a little bit deeper, Mavroeidis et al.
-introduce the reader to present cryptography algorithms, how they are vulnerable to quantum computers and about their main topic, post quantum security \cite{DBLP:journals/corr/abs-1804-00200}.
+introduce the reader to present cryptography algorithms, how they are vulnerable to quantum computers and their main topic, post quantum security \cite{DBLP:journals/corr/abs-1804-00200}.
 
@@
 Quantum computers utilize qubits to represent information. 
-Instead of working with a stream of electiral or optical signals representing 1s and 0s, 
+Instead of working with a stream of electrical or optical signals representing 1s and 0s, 
 quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
@@
 These disturbances can be caused by vibrations, change of temperatures or related external influences.
-Disturbances are also refered to as "noise" in quantum computer terminology.
-Decoherence is the reason why qubits quantum computers are held in extremly protected environments, 
+Disturbances are also referred to as "noise" in quantum computer terminology.
+Decoherence is the reason why qubits are held in extremly protected environments, 
 often fridges or vacuum chambers.
@@
 thousands of standard qubits will be needed to create a reliable qubit, 
-refered to as a "logical" qubit. 
+referred to as a "logical" qubit. 
 A logical qubit has a long enough coherence time to be used for quantum logic gates. 
-Essentially, logical qubits are a group of regular qubits refered to as a singular qubit in computation, 
+Essentially, logical qubits are a group of regular qubits referred to as a singular qubit in computation, 
 which have more stable characteristics than regular qubits.
@@
 Since the first proposals revolving around quantum computers by Yuri Manin in 1980 and Richard Feynman in 1981,
-the term "quantum supremacy" is used to denote the point at which a quantum computer can complete a mathematic calculation that is beyond reach of even the most powerful supercomputers.
+the term "quantum supremacy" is used to denote the point at which a quantum computer can complete a mathematical calculation that is beyond reach of even the most powerful supercomputers.
 It is unclear how many qubits will be needed to achieve superposition. 
@@
 
-Potential applications for quantum computer exceed cryptography.
+Potential applications for quantum computers exceed cryptography.
 Some potential applications include the simulation of quantum systems, machine learning, computational biology and generative chemistry.
-
-There is not a single way to build a quantum computer. 
-Instead, different approaches can be followed to develop machines utilizing quantum effects for computing. Some of which will be discussed in the following section.
 \end{section}
@@
 
-There are different approaches to realize quantum computers.
+There are different approaches on how to realize machines utilizing quantum effects for computing known as quantum computers.
 Those different approaches have different advantantages and challenges. 
@@
 The distance of a few wavelengths is sufficient to operate each ion with a different laser. 
-A challenge the researchers faced when trying to realize an ion trap is the mechanical degree of freedom the ions have. 
+A challenge the researchers are faced with when trying to realize an ion trap is the mechanical degree of freedom the ions have. 
 In general, the ions are trapped at their position but they are in fact not resting but oscillating around their equilibrium position. 
@@
 
-The ion trap could demonstrate the fundamental operations of a quantum computer with the highest accuracy so far. 
-Ion trap quantum computers are researched because they could potentially be used for a large-scale quantum computer as scaling the ion trap to a large number of qubits could be accomplished by combining multiple ion traps into an array.
-Ions then could be transported between the ions traps.
-As of 2018, the largest number of particles to be controllable entangled is 20 trapped ions. 
-In 2021, scientists from the University of Innsbruck presented a quantum computer based on the ion trap that fits inside two 19-inch server racks.
+In 2018, Nicolai Friis et al. controllably entangled 20 trapped ions as they describe in their paper \cite{friis}.
 \end{subsection}
@@
 \begin{subsection}{Nuclear Magnetic Resonance}
-As explained in the article by Gershenfeld \cite[p.66-71]{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and a nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
-Each molecule in the liquid represents an quantum memory register. 
+As explained in the article by Gershenfeld \cite[p.66-71]{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) quantum computer consists of a capsule filled with a liquid and a nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
+Each molecule in the liquid represents a quantum memory register. 
 NMRs can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
@@
 In contrast to the ion trap quantum computer, 
-a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register.
+a measurement is performed on a statistical ensemble of molecules instead of a single isolated one.
 
@@
 
-Solid state NMR (SSSNMR) differ from LSNMR in that SSSNMR provide a solid state sample.
+Solid state NMRs differ from LSNMRs in that SSSNMRs provide a solid state sample.
 This has many advantages such as lack of molecular diffusion coherence and lower temperatures, as well as the more precise localization of qubits using crystal structures.
@@
 This tunneling produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
-This is used to create a non-linear inductance and design the qubits. 
+Said current is used to create a non-linear inductance. 
 Wendin and Shumeiko mention \cite[p.727]{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
 The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
-The josephson energy comes from kinetic energy of the tunneling electrons.
+The josephson energy is the kinetic energy of tunneling electrons in the system.
 
@@
 \begin{section}{Challenges in Quantum Computing}
-As of 2021, there are some challenges researcher in the current state of quantum computing which can be derived from the earlier chapters:
+As of 2021, there are some challenges researchers face in the current state of quantum computing which can be derived from the earlier chapters:
 
@@
 in the Josephson junction quantum computer, extremely low temperatures are needed.
-These have to be achieved at reasonable cost.
+These have to be achieved at a reasonable cost.
 Using e.g.
-laser cooling is a one approach in quantum computing.
+laser cooling is one approach in quantum computing.
 The concept of laser cooling was proposed by Steven Chu, Claude-Cohen-Tannoudji and William D.
@@
     Noise can be caused e.g. by heat or noise in the environment. 
-    As in classical computing, this noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
+    As in classical computing, noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
     One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
-    \item Increasing the number of qubits in a processor.
+    \item Increasing the number of qubits in a processor is fundamental.
 The more qubits in a processor, the more logical qubits can be used.
@@
 also known as a quantum birthday attack, which leads to finding collisions with a complexity of $O(N^{\frac{1}{3}})$.
-As a result, many of current , rather weak, hashing alogithms are disqualified for use in the quantum era. 
-However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant as even Grover's algorithm does not make it feasible to to find a collision when the keys are too long.
+As a result, many of current, rather weak, hashing algorithms are disqualified for use in the quantum era. 
+However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant as even Grover's algorithm does not make it feasible to find a collision when the keys are too long.
 \end{subsection}
@@
 \begin{subsection}{Improve Current Security Mechanisms}    
-Improving current security mechanisms by increasing the key length from 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search unsing Grover's algorithm. 
+Improving current security mechanisms by increasing the key length from 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm. 
 The speedup Grover's algorithm provdides is not that efficient as that it could crack this key in a feasible amount of time.
@@
 As Micciancio and Regev mention in their paper \cite[p.2]{Micciancio2009}, 
-lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems and it is belived that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,
+lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems.
+It is belived but not proven that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,
 which is used in Shor's algorithm cannot be used in lattice-based problems. 
@@
 like lattice-based cryptography. 
-Even the huge speedups quantum-computers provide don't make it feasible to crack these algorithms. 
+Even the huge speedups quantum-computers provide do not make it feasible to crack these algorithms. 
 It is not known yet, which type of quantum computer will prevail. 

### 2022-01-08 paper.tex
feat: Final corrections

@@
 Prashant writes about the limitations of classical computers and how quantum computers can be realized \cite{prashant}. 
-Their brief explanations on different realizations of quantum computers is introducing the reader to several related research areas on a high level.
+Their explanations on different realizations of quantum computers are introducing the reader to several related research areas on a high level.
 
-Providing detailed examples of the workings of Shor's and Grover's algorithm are Bone and Castro in their overview of quantum computing \cite{Bone}.
+Providing examples of the workings of Shor's and Grover's algorithm are Bone and Castro in their overview of quantum computing \cite{Bone}.
 
-Vedral and Planio provide an especially interesting and detailed explanation of ion trap quantum computers in their paper \cite{2008}.
+Vedral and Planio provide a detailed explanation of ion trap quantum computers in their paper about the fundamentals of quantum computing \cite{2008}.
 
@@
 
-Diving a little bit deeper, Mavroeidis et al.
+Mavroeidis et al.
 introduce the reader to present cryptography algorithms, how they are vulnerable to quantum computers and their main topic, post quantum security \cite{DBLP:journals/corr/abs-1804-00200}.
@@
 Quantum computers utilize qubits to represent information. 
-Instead of working with a stream of electrical or optical signals representing 1s and 0s, 
+Instead of working with classical bits representing 1s and 0s, 
 quantum computers utilize qubits, which can represent various combinations of 1s and 0s at the same time. 
-This effect is called superposition. To put qubits into superposition, 
+This effect of qubits representing multiple states at the same time is called superposition. To put qubits into superposition, 
 researchers manipulate qubits in different ways. As quantum computing is based on quantum mechanics and hence has to obey to the same laws, 
@@
 
-\begin{section}{Experimental Realizations of Quantum Computers}
+\begin{section}{Realizations of Quantum Computers}
 
@@
 
-Solid state NMRs differ from LSNMRs in that SSSNMRs provide a solid state sample.
-This has many advantages such as lack of molecular diffusion coherence and lower temperatures, as well as the more precise localization of qubits using crystal structures.
+Solid state NMRs differ from LSNMRs in that SSSNMRs provide a sample in solid state.
+This has many advantages such as being able to work using lower temperatures as well as the more precise localization of qubits using crystal structures.
 In SSNMRs, qubits can be measured individually, same as in the ion trap,
-instead of having to measure an ensemble of molecules as in LSNMR.
+instead of having to measure an ensemble of molecules as in LSNMRs.
 
@@
     \item Often, as e.g.
-in the Josephson junction quantum computer, extremely low temperatures are needed.
+in the Josephson junction quantum computer, extremely low temperatures are required.
 These have to be achieved at a reasonable cost.
@@
     Noise can be caused e.g. by heat or noise in the environment. 
-    As in classical computing, noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
+    As in classical computing, noise can lead to bit-flips. There are approaches in "quantum error correction" to deal with these errors. 
     One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
@@
 
-% Research for this paragraph and add some more post quantum crypto examples
 \begin{section}{Post Quantum Cryptography}

### 2022-04-19 paper.tex
refactor: Cleanup
fix: Typos

@@
 \documentclass[aps,preprintnumbers,twocolumn]{revtex4}
-% \documentclass[aps,preprintnumbers]{scrartcl}
 \usepackage{natbib}
@@
 
-\affiliation{\it Stuttgart Media University, 70569 Stuttgart}
+\affiliation{\it Stuttgart Media University, Stuttgart}
 
@@
 This paper aims to inform readers about the topic on a high-level to be able to join the discussion about the future relevance of quantum computing.
-First, this paper will explain the basics of quantum computing and dive into types of quantum computers including ion traps, nuclear magnetic resonance quantum computers and quantum computers based on josephson junctions.
+First, this paper will explain the basics of quantum computing and dive into types of quantum computers including ion traps, nuclear magnetic resonance quantum computers and quantum computers based on Josephson junctions.
 Afterwards, the effects of quantum computing algorithms, especially Shor's and Grover's algorithm on current security mechanisms are discussed, rounding off by explaining approaches on how to achieve post quantum security.
@@
 quantum computing has become a large research area. 
-Even so large, that it has become more and more difficult to understand the basics of it and its implications on the future of computing. 
+Quantum computing has become even so large, that it has become more and more difficult to understand the basics of it and its implications on the future of computing. 
 This work will introduce the reader to the basics of quantum computing from a computer scientists perspective. 
@@
 Prashant writes about the limitations of classical computers and how quantum computers can be realized \cite{prashant}. 
-Their explanations on different realizations of quantum computers are introducing the reader to several related research areas on a high level.
+Their explanations on different realizations of quantum computers introduce the reader to several related research areas on a high level.
 
-Providing examples of the workings of Shor's and Grover's algorithm are Bone and Castro in their overview of quantum computing \cite{Bone}.
+Bone and Castro provide examples of the workings of Shor's and Grover's algorithm in their overview of quantum computing \cite{Bone}.
 
-Vedral and Planio provide a detailed explanation of ion trap quantum computers in their paper about the fundamentals of quantum computing \cite{2008}.
+Vedral and Planio explain ion trap quantum computers in their paper about the fundamentals of quantum computing \cite{2008}.
 
-Martinis and Osborne write about josepshon junctions \cite{martinis} and how the josephson effect can be used to create a quantum computer utilizing superconductors.
+Martinis and Osborne write about Josephson junctions \cite{martinis} and how the Josephson effect can be used to create a quantum computer utilizing superconductors.
 
@@
 a measurement determines the state of a qubit. Once qubits are measured, 
-its quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.
+their quantum state immediately collapses to either 1 or 0 and its state of superposition is lost.
 
@@
 As Alamira Jouman Hajjar puts it in her Article on AIMultiple \cite{AIMultiple}, one qubit will reveal information about all the qubits said qubit is entangled with.
-This entanglement allows quantum computers to increase its computational power exponentially,
-rather than linearly on regular computers.
-According to an article of IEEE Spectrum \cite{IEEE}, a quantum computer equipped with 300 qubits could represent more states than there are atoms in the observable universe.
+This entanglement allows quantum computers to increase their computational power exponentially,
+rather than linearly as regular computers.
+According to an article in IEEE Spectrum \cite{IEEE}, a quantum computer equipped with 300 qubits could represent more states than there are atoms in the observable universe.
 
@@
 Decoherence is the reason why qubits are held in extremly protected environments, 
-often fridges or vacuum chambers.
-To compensate for this noise, 
+often refrigerators or vacuum chambers.
+To compensate for noise, 
 thousands of standard qubits will be needed to create a reliable qubit, 
@@
 It is unclear how many qubits will be needed to achieve superposition. 
-This results out of the fact that research results in new algorihtms and hardware improvements to boost the performance of classical (super)computers.
+This results from the fact that research results in new algorihtms and hardware improvements to boost the performance of classical (super)computers.
 
 Potential applications for quantum computers exceed cryptography.
-Some potential applications include the simulation of quantum systems, machine learning, computational biology and generative chemistry.
+Some potential applications include the simulation of quantum systems, machine learning, computational biology, generative chemistry and optimization problems.
 \end{section}
@@
 Each molecule in the liquid represents a quantum memory register. 
-NMRs can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
+NMR based quantum computers can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
 In an NMR quantum computer, qubits are represented as spin states of the atoms in the molecules. 
@@
 
-Initially, as mentioned above, the NMRs used atoms in a liquid sample as qubits which is known as liquid state NMR (LSNMR). 
+Initially, as mentioned above, the NMR based quantum computer used atoms in a liquid sample as qubits which is known as liquid state NMR (LSNMR). 
 Since solid state NMRs (SSNMR) emerged, SSNMR is usually preferred in terms of performing quantum computation.
 
-Solid state NMRs differ from LSNMRs in that SSSNMRs provide a sample in solid state.
+Solid state NMRs differ from LSNMRs in that SSNMRs provide a sample in solid state.
 This has many advantages such as being able to work using lower temperatures as well as the more precise localization of qubits using crystal structures.
@@
 Said current is used to create a non-linear inductance. 
-Wendin and Shumeiko mention \cite[p.727]{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
+Wendin and Shumeiko mention \cite[p.727]{shumeiko} many ways to realize qubits in quantum computers based on Josephson junctions. 
 The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
-The josephson energy is the kinetic energy of tunneling electrons in the system.
+The Josephson energy is the kinetic energy of tunneling electrons in the system.
 
@@
 \begin{section}{Challenges in Quantum Computing}
-As of 2021, there are some challenges researchers face in the current state of quantum computing which can be derived from the earlier chapters:
+As of 2021, there are some challenges researchers face in the current state of quantum computing which can be derived from the earlier sections:
 
@@
 \begin{subsection}{Shor's algorithm}
-Shor's algorithm is a quantum computer algorithm and got developed by Peter Shor in 1994.
+Shor's algorithm is a quantum computer algorithm developed by Peter Shor in 1994.
 Essentially, it can find the prime factors of an integer in the complexity class BQP,
@@
 Think of all possible permutations of $n$ bits existing in parallel.
-A calculation performed with Shor's algorithm can be thought of as computations done in parallel for every of the permutations generated before. 
+A calculation performed with Shor's algorithm can be thought of as computations done in parallel for every permutation generated before. 
 They then describe the mathematics performed on the registers: 
@@
 After performing these operations on all permutations, it is noticable that the contents of the second register repeat e.g. for $N = 15$ the repeating sequence would be $1,2,4,8,1,2,4...$.
-Now the frequency of repetition can be calculated by using a complex operation on the second register and the looking at the contents which causes the results from every permutation to interfere.
+Now the frequency of repetition can be calculated by using a complex operation on the second register and looking at the contents which causes the results from every permutation to interfere.
 A possible prime factor can then be calculated by using the frequency of repetition $f$:
@@
 \end{equation}
-The inteference that provides $f$ will lead to the correct answer with a high probability as incorrect answers cancel each other out when interfering.
-This cannot be guaranteed!
+The interference that provides $f$ will lead to the correct answer with a high probability as incorrect answers cancel each other out when interfering.
+This cannot be guaranteed.
 Checking that the resulting number is correct can be achieved by performing a simple multiplication.
@@
 The analogous problem in classical computing has $O(N)$ complexity. 
-Grover's algorithm is achieving the same goal in $O(\sqrt{N})$. 
+Grover's algorithm achieves the same goal in $O(\sqrt{N})$. 
 In contrast to Shor's algorithm providing exponential speedup, 
@@
 Improving current security mechanisms by increasing the key length from 128 bits to 256 bits squares the number of possible permutations a quantum computer has to search using Grover's algorithm. 
-The speedup Grover's algorithm provdides is not that efficient as that it could crack this key in a feasible amount of time.
+The speedup Grover's algorithm provdides is not efficient enough to crack this key in a feasible amount of time.
 \end{subsection}
@@
 Another approach would be to develop new algorithms using more complex trapdoor functions even quantum computers could not possibly crack in a feasible amount of time. 
-Researchers are working in areas like lattice-based cryptography, supersingular isogeny key exchange or hash-based cryptography. One of these approaches will be described in the following:
+Researchers are working in areas like lattice-based cryptography, supersingular isogeny key exchange or hash-based cryptography. One of these approaches is described in the following:
 
@@
 It is belived but not proven that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,
-which is used in Shor's algorithm cannot be used in lattice-based problems. 
+which is used in Shor's algorithm, cannot be used in lattice-based problems. 
 \end{subsubsection}
@@
 like lattice-based cryptography. 
-Even the huge speedups quantum-computers provide do not make it feasible to crack these algorithms. 
+Even the speedups quantum-computers provide do not make it feasible to crack these algorithms. 
 It is not known yet, which type of quantum computer will prevail. 
-Ion traps, Nuclear Magnetic Resonance and Josepshon Junctions are some of the most promising approaches. 
+Ion traps, Nuclear Magnetic Resonance and Josepshon junctions are some of the most promising approaches. 
 In current systems like the IBM Q System One, 
@@
 If this approach will prevail is unclear, 
-since quantum entanglement in this type of processor is, as of 2021, not possible yet. 
-It has to be said that quantum computers, 
-as what could be seen in current records,  
-are not powerful enough to form a thread to security mechanisms by now, 
+since quantum entanglement in this type of processor is not possible as of 2021. 
+Quantum computers, 
+as current records depict,  
+are not powerful enough to form a threat to security mechanisms by now, 
 since way more qubits are needed to perform operations on large enough numbers and preserve the state of superposition long enough. 
-To conclude, it should be said that quantum computing should be seen as an opportunity for overdue improvement, not as a thread to digital security. 
+To conclude, it should be said that quantum computing should be seen as an opportunity for overdue improvement, not as a threat to digital security. 
 \end{section}

### 2022-04-20 docs/quantum_computing.tex
fix: Citations

--- 2022-04-19 paper.tex
@@
 \usepackage{url}
+\usepackage{filecontents}
 
@@
 
+\begin{filecontents}{citations.bib}
+@internet{IEEE,
+  author = {IEEE Spectrum},
+  title = {How Many Qubits Are Needed for Quantum Supremacy?},
+  year = 2020,
+  howpublished = {\url{https://spectrum.ieee.org/qubit-supremacy}},
+  urldate = {2022-01-05}
+}
+
+@internet{AIMultiple,
+  author = {AIMultiple},
+  title = {Quantum Entanglement: What it is \& Why it is important},
+  year = 2021,
+  howpublished = {\url{https://research.aimultiple.com/quantum-computing-entanglement/}},
+  urldate = {2022-01-05}
+}
+
+@internet{MIT,
+  author = {MIT Technology Review},
+  title = {This new startup has built a record-breaking 256-qubit quantum computer},
+  year = 2021,
+  howpublished = {\url{https://www.technologyreview.com/2021/11/17/1040243/quantum-computer-256-bit-startup/}},
+  urldate = {2022-01-05}
+}
+
+@article{DBLP:journals/corr/abs-1804-00200,
+  author    = {Mavroeidis and
+               Vishi and
+               Zych and
+               J{\o}sang},
+  title     = {The Impact of Quantum Computing on Present Cryptography},
+  journal   = {CoRR},
+  year      = {2018},
+  url       = {http://arxiv.org/abs/1804.00200},
+  eprinttype = {arXiv},
+  eprint    = {1804.00200},
+  timestamp = {Mon, 13 Aug 2018 16:46:41 +0200},
+  biburl    = {https://dblp.org/rec/journals/corr/abs-1804-00200.bib},
+  bibsource = {dblp computer science bibliography, https://dblp.org}
+}
+
+@inproceedings{Kirsch2015QuantumCT,
+  title={Quantum Computing: The Risk to Existing Encryption Methods},
+  author={Kirsch and Chow},
+  year={2015}
+}
+
+@article{article,
+author = {Martín-López and Laing and Lawson and Alvarez and Zhou and O'Brien},
+year = {2011},
+pages = {},
+title = {Experimental realisation of Shor's quantum factoring algorithm using
+qubit recycling},
+journal = {Nature Photonics},
+doi = {10.1038/nphoton.2012.259}
+}
+
+@article{1998,
+   title={Quantum cryptanalysis of hash and claw-free functions},
+   ISSN={1611-3349},
+   url={http://dx.doi.org/10.1007/BFb0054319},
+   DOI={10.1007/bfb0054319},
+   journal={Lecture Notes in Computer Science},
+   publisher={Springer Berlin Heidelberg},
+   author={Brassard and HØyer and Tapp},
+   year={1998},
+   pages={163–169}
+}
+
+@article{2008,
+   title={Basics of quantum computation},
+   volume={22},
+   ISSN={0079-6727},
+   url={http://dx.doi.org/10.1016/S0079-6727(98)00004-4},
+   DOI={10.1016/s0079-6727(98)00004-4},
+   number={1},
+   journal={Progress in Quantum Electronics},
+   publisher={Elsevier BV},
+   author={Vedral and Plenio},
+   year={2008},
+   month={Jan},
+   pages={1–39}
+}
+
+@article{prashant,
+author = {Prashant},
+year = {2005},
+journal = {},
+pages = {},
+title = {A Study on the basics of Quantum Computing}
+}
+
+@article{Gershenfeld1998QuantumCW,
+  title={Quantum Computing with Molecules},
+  author={Gershenfeld and Chuang},
+  journal={Scientific American},
+  year={1998},
+  volume={278},
+  pages={66-71}
+}
+
+@article{shumeiko,
+author = {Wendin and Shumeiko},
+year = {2007},
+pages = {957-981},
+title = {Quantum bits with Josephson junctions},
+journal = {Fizika Nizkikh Temperatur (Kharkov)}
+}
+
+@article{martinis,
+author = {Martinis and Osborne},
+year = {2004},
+title = {Superconducting Qubits and the Physics of Josephson Junctions},
+journal = {}
+}
+
+@article{Bone,
+author = {Bone and Castro},
+year = {2017},
+title = {A Brief History of Quantum Computing}, 
+journal = {}
+}
+
+@article{Micciancio2009,
+author="Micciancio
+and Regev",
+title="Lattice-based Cryptography",
+year="2009",
+publisher="Springer Berlin Heidelberg",
+address="Berlin, Heidelberg",
+isbn="978-3-540-88702-7",
+doi="10.1007/978-3-540-88702-7_5",
+url="https://doi.org/10.1007/978-3-540-88702-7_5"
+}
+
+@article{friis,
+  title = {Observation of Entangled States of a Fully Controlled 20-Qubit System},
+  author = {Friis, Nicolai and Marty, Oliver and Maier, Christine and Hempel, Cornelius and Holz\"apfel, Milan and Jurcevic, Petar and Plenio, Martin B.
+and Huber, Marcus and Roos, Christian and Blatt, Rainer and Lanyon, Ben},
+  journal = {Phys. Rev. X},
+  issue = {2},
+  numpages = {20},
+  year = {2018},
+  publisher = {American Physical Society},
+  doi = {10.1103/PhysRevX.8.021012},
+  url = {https://link.aps.org/doi/10.1103/PhysRevX.8.021012}
+}
+\end{filecontents}
+
 \end{document}
